Novelty Detection Using Graphical Models for Semantic Room Classification

### 2011-05-17 semantic-nd/article.tex
Fixed comments on unconditional probabilities sections.

In the presented case the conditional probability is approximated by the graphical model $G$
produced by the conceptual layer.
\autoref{fig:conditional-prob-graph} represents a possible graph $G$ built from the conceptual
layer to represent the conditional probability on the sensed variables $x$.
$P_G(x)$ is used as an approximation for $P(x|\overline{novel})$.

@@

\subsection{Semi Supervised: Using Unlabelled Data}
Nonetheless its often the case that there is access to large amounts of unlabelled data.
Under that it becomes possible to obtain a better approach to the unconditional probability
distribution than the uniform one.

For interesting and practical reasons it was assumed that the unconditional distribution
could be modelled with all the variables independent from each other.
Which translates as $P(x)=\prod{P_{x_i}(x_i)}$.
From the unlabelled data only the probability of each feature $x_i$ needs to be estimated.
\autoref{fig:semisupervised-threshold} illustrates a graph $I$ to model independent variables.

@@

Once again the novelty threshold would be given by $P_G(x)/P_I(x)$.
This time the addition of the variables unconditional factors can be understood as an
attempt to compensate for an existing bias on the unconditional distribution.
Which is an important step to achieve a correct ordering of the input space for novelty
thresholding.

>>>>

In the presented case, the conditional probability is approximated by the graphical model $G$
produced by the conceptual layer.
\autoref{fig:conditional-prob-graph} represents a possible graph $G$ built from the conceptual
layer to represent the conditional probability on the sensed variables $x$.
$P_G(x)$ is used as an approximation for $P(x|\overline{novel})$.

@@

\subsection{Semi Supervised: Using Unlabelled Data}
Nonetheless, its often the case that there is access to large amounts of unlabelled data.
Under that it becomes possible to obtain a better approach to the unconditional probability
distribution than the uniform one.

For practical reasons it was assumed that the unconditional distribution
could be modelled with all the variables independent from each other.
Which translates as $P(x)=\prod{P_{x_i}(x_i)}$.
From the unlabelled data, only the probability of each feature $x_i$ needs to be estimated.
\autoref{fig:semisupervised-threshold} illustrates a graph $I$ to model independent variables.

@@

Once again the novelty threshold would be given by $P_G(x)/P_I(x)$.
This time the addition of the unconditional factors can be understood as an
attempt to compensate for an existing bias on the unconditional distribution.
This is an important step to achieve a correct order-relation of the inputs sample
for implementing a novelty threshold.
